---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    linkcolor: darkgray
    urlcolor: teal
    documentclass: scrartcl
    papersize: A4
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - code/preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

# knitr::opts_chunk$set(
#   fig.path = "figs/",
#   fig.width = 7.252,
#   fig.height = 4,
#   comment = "#>",
#   fig.retina = 3
# )

Sys.setlocale("LC_TIME", "en_US.UTF-8")

source("code/functions.R")

# Store IDs
gscholar_id <- 'EdZjQtsAAAAJ&hl'
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)
orcid_id = "0000-0002-2531-4175"
orcid_page = paste0("https://orcid.org/", orcid_id)


# TODO
# check if ordering is consistent - recent first.
# to numbered lists with highest number first. 
# adjust education table to academic appointment table.
# add affiliated grants -- DONE
# add #citations -- DONE
```

\begin{center}
{\LARGE Dr. Martin Schoemann}\par
Psychological Research Methods \& Cognitive Modeling\par
\vspace{-5pt}
School of Science -- Faculty of Psychology\par
\vspace{-5pt}
TUD Dresden University of Technology\par
\vspace{-5pt}
BZW, Office A322\par
\vspace{-5pt}
Zellescher Weg 17, Dresden, D-01069\par
\vspace{-5pt}
{\large\Telefon} +49 (351) 463-32467\par
\vspace{-5pt}
{\large\Letter} martin.schoemann[at]tu-dresden.de\par
%\vspace{-5pt}
%\href{http://www.mschoemann.com}{www.mschoemann.com}
\end{center}

\vspace{-10pt}

# Academic Appointments

\vspace{-10pt}
\begin{longtable}{llp{15cm}}

2022 -- present & \textbf{TUD Dresden University of Technology}, Dresden, Germany \\
 & Research Associate, Psychological Research Methods and Cognitive Modelling\\[5pt]

2020 -- 2022 & \textbf{Aarhus University}, Aarhus, Denmark \\
 & Research Assistant, Management\\[5pt]

2016 -- 2020 & \textbf{TUD Dresden University of Technology}, Dresden, Germany \\
 & Predoctoral Researcher, Psychological Research Methods and Cognitive Modelling \\
 & and CRC 940 \emph{Volition and Cognitive Control}
\end{longtable}

\vspace{-10pt}


# Education & Training

\vspace{-10pt}
\begin{longtable}{lll}

2025 & TUD Dresden University of Technology, Dresden, Germany & \textbf{Dr. rer. nat. (PhD) Psychology}\\

\multicolumn{3}{p{16cm}}{Dissertation: \emph{The Trouble with Reverse Inference: On the Mapping between Decision Processes and Movement Dynamics}}\\

\multicolumn{3}{p{16cm}}{Doctoral Committee: \emph{Stefan Scherbaum, Andreas Glöckner, Sebastian Pannasch, \& Alexander Strobel}}\\[5pt]
    
2016 & Erfurt University, Erfurt, Germany & \textbf{M. Sc. Psychology}\\
    
\multicolumn{3}{p{16cm}}{Thesis: \emph{Distinguishing Comparison Strategies in Intertemporal Decision Making: An Eye-tracking Study}}\\
    
\multicolumn{3}{p{16cm}}{Advisors: \emph{Frank Renkewitz \& Stefan Scherbaum}}\\[5pt]

2013 & Erfurt University, Erfurt, Germany & \textbf{B. A. Psychology \& Philosophy}\\
    
\multicolumn{3}{p{16cm}}{Thesis: \emph{Small Sample Advantage in Complex Environments: On the Detection of Population Parameters in the Iowa Gambling Task}}\\
    
\multicolumn{3}{p{16cm}}{Advisor: \emph{Tilmann Betsch}}\\[10pt]

2024 & Hochschudidaktik Sachsen, Leipzig, Germany & \textbf{Cert. Teacher of HE}\\

\multicolumn{3}{p{16cm}}{Thesis: \emph{Reducing Cognitive Load while Simultaneously Teaching Statistics and Programming Skills}}\\



\end{longtable}

\vspace{-10pt}


# Research Interests

- **Process Dynamics in Judgement and Decision Making**: Exploring the temporal dynamics of cognitive and affective processes underlying human judgment and decision making.
- **Methods of Process Tracing**: Developing and applying process-tracing methods to uncover temporal dynamics of cognitive processes underlying human behavior.
- **Cognitive Modeling (DDM, ABM, DFT)**: Using formal cognitive models such as Drift Diffusion Model, Agent-Based Modeling, and Dynamic Field Theory to simulate and explain the cognitive processes driving human behavior.
- **Behavior Change**: Investigating psychological drivers and interventions that promote sustainable and health-related change in human behavior.
- **Meta-science**: Examining the practices, methods, and structures of psychological science to improve research transparency, reproducibility, and cumulative knowledge building.

\vspace{-10pt}


# Teaching Interests

- **Psychological Research Methods**: Teaching rigorous research design and methodology to foster critical thinking, transparency, and reproducibility in psychological science.
- **Statistics**: Introducing statistical reasoning and providing hands-on training on tools for analyzing psychological data in a reproducible manner.
- **Programming \& Data Science**: Providing hands-on training for programming and data analytics in R and MATLAB for transparent, reproducible, and efficient handling, visualization, evaluation of psychological data.
- **Cognitive Modeling**: Introducing formal modeling techniques to stimulate better reasoning and theory building in psychological science.
- **Meta analysis \& Meta studies**: Teaching methods for synthesizing evidence across studies and to establish robust and generalizable psychological research findings.



# Publications

<!-- Set spacing in between list -->
<!-- \apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{} -->

\begin{center}
ORCID: \href{https://orcid.org/0000-0002-2531-4175}{0000-0002-2531-4175} | \href{https://scholar.google.com/citations?user=EdZjQtsAAAAJ&hl=en}{Google Scholar Profile}

`{r} gscholar_stats(gscholar_id)`

\* indicates equal contribution
\end{center}

<!-- \begin{small} -->
<!-- \emph{Note on author order: In my field, it is conventional that the last author denotes intellectual direction by the senior author when advised student(s) are engaged on the study. On non–student papers, authorship effort is denoted in standard order}. -->
<!-- \end{small} -->

## Refereed Journal Articles

```{r}
pubs <- get_cv_sheet('pubs') |> 
    left_join(
        gscholar_cites(gscholar_id),
        by = "id_scholar"
    ) |>
    mutate(
        journal = ifelse(is.na(journal), '', paste0('_', journal, '_,')),
        number = ifelse(is.na(number), '', paste0(number, '.')),
        doi = if_else(
            is.na(doi), "",
            paste0("DOI: [", doi, "](", "https://doi.org/", doi, ").")
        ),
        year = paste0("(", year, ")."),
        title = paste0(title,"."),
        cites = if_else(
            is.na(cites), '',
            paste0(" Citations (#): ", cites, '.'),
        ),
        citation = paste(author, year, title, journal, number, doi, cites),
    ) |> 
    arrange(
        # desc(pub_date),
        desc(year),
        gsub("[^A-Za-z0-9 .,&']", "", author)
    )
```

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "peer_reviewed")
```


## Working Papers & Papers Under Review

```{r}
#| results: asis

make_ordered_list_filtered(pubs, "working")
```


# Presentations / Conferences
```{r}
pres = get_cv_sheet('presentations') |> 
    mutate(
        with = ifelse(is.na(with), '.', paste0(', with ', with)),
        title = paste0(enquote(title), with),
        # title = paste0("*", title, "*", with),
        title = ifelse(is.na(series), title, paste(title, series, sep = '. ')),
        host = if_else(
            category == "poster",
            paste0("Poster presented at ", host),
            paste0("Talk presented at ", host)
        ),
        date = paste0(format(as.Date(date), format = "%Y"), '.'),
        citation = paste0(title, ' ', host, ', ', location, '. ', date)
    ) |> 
    arrange(desc(date))

pres_counts = pres |>
    count(category) |>
    left_join(
        data.frame(
            category = c("invited", "conference", "poster"),
            order = seq(3)
        ),
        by = "category"
    ) |>
    mutate(
        category = str_to_title(category),
        category = ifelse(category == 'Invited', 'Invited Speaker', category),
        category = ifelse(category == 'Conference', 'Conference Presentation', category),
        category = ifelse(category == 'Poster', 'Poster Presentation', category),
        cite = paste0(category, ' (', n, ')')
    ) |>
    arrange(order) |>
    pull(cite) |>
    paste(collapse = ', ')
```

\begin{center}
\textit{Total Presentations by Category}

`r pres_counts`
\end{center}

<!-- ## Invited Speaker -->

<!-- ```{r} -->
<!-- #| results: asis -->

<!-- make_ordered_list_filtered(pres, "invited") -->
<!-- ``` -->


## Conference Presentations

```{r}
#| results: asis

make_ordered_list_filtered(pres, "conference")
```


## Posters

```{r}
#| results: asis

make_ordered_list_filtered(pres, "poster")
```


# Teaching & Education


## Courses Taught at TUD Dresden University of Technology
```{r}
df = get_cv_sheet('classes') |>
    mutate(
      course = paste0(number, ": ", name),
      score = paste0(specdec(mean,2)," (",specdec(dept_mean,2),")"),
      # num = paste(responses, '/', enrolled),
      # score = paste(inst_mean, '/', dept_mean),
      # semester = ifelse(semester == 'S20', 'S20$^†$', semester)
      role = str_to_title(role)
    ) |> 
    select(
      `Sem.` = semester,
      Course = course,
      Role = role,
      Type = type,
      Level = level,
      `N. Resp.` = responses,
      `Instr. FCE*` = score,
    )

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") |> 
  column_spec(2, width = "6cm") |>
  # column_spec(7, width = "2cm") |> 
  footnote(
      general_title = "",
      general = "F = Fall, denotes the winter term, Oct.--Mar.; S = Spring, denotes the summer term, Apr.--Sep.",
      # symbol = "Evaluation results on request."
    symbol = c(
        "Faculty Course Evaluations (FCE) for `Overall satisfaction` scored 1--5 (1 = best). Complete evaluation sheets are available upon request."
    ),
    threeparttable = TRUE
)
```

```{r}
teaching <- get_cv_sheet('teaching') %>%
  arrange(desc(date)) %>%
  mutate(
    with = ifelse(is.na(with), '', paste0(', with ', with)),
    title = paste0(enquote(title), with),
    date = paste0(format(as.Date(date), format = "%b %d, %Y"), '.'),
    url = ifelse(is.na(url), NA, markdown_url(url)),
    date = ifelse(is.na(url), date, paste0(date, '. ', url)),
    citation = paste0(title, ' ', host, ', ', location, '. ', date)
  )
```


## Workshops

```{r}
#| results: asis

make_ordered_list_filtered(teaching, "workshop")
```


## Guest Lectures

```{r}
#| results: asis

make_ordered_list_filtered(teaching, "guestlecture")
```


# Advising
```{r}
advisees <- get_cv_sheet('advising') |> 
    mutate(
        date = case_when(
            complete == 0 ~ ' (current).',
            is.na(date_stop) ~ '.',
            is.na(date_start) ~ paste0(' (', date_stop, ').'),
            .default = paste0(' (',  date_start, ' to ', date_stop, ').')
        ),
        # date_start = if_else(is.na(date_start), date_stop, date_start),
        with = ifelse(is.na(with), '', paste0(', with ', with)),
        citation = if_else(
            is.na(title), name, paste0(name, ', ', enquote(title))
        ),
        citation = paste0(citation, ', ', institution, with, date),
        citation = if_else(
            is.na(defense_date),
            citation,
            paste0(citation, ' _Defense date: ', defense_date, '_.')
        )
    ) |> 
    arrange(date_start, name)
```


## Doctoral Students
```{r}
#| results: asis

advisees |>
  make_ordered_list_filtered("dr")
```

## Master's Students

```{r}
#| results: asis

advisees |>
  make_ordered_list_filtered("ma")
```


## Bachelor's Students

```{r}
#| results: asis

advisees |>
  make_ordered_list_filtered("ba")
```


## Interns

```{r}
#| results: asis

advisees |>
  make_ordered_list_filtered("intern")
```


# Grants

```{r}
grants <- get_cv_sheet('grants') |> 
    filter(awarded == 1) |> 
    mutate(
        sponsor = if_else(
            !is.na(id),
            paste0(sponsor, " (No. ", id, ")"),
            sponsor
        ),
        title = enquote(title),
        amount = if_else(
            is.na(budget_total), 
            "",
            label_euro(budget_total)
        ),
        percent = budget_me / budget_total,
        credit = case_when(
            percent == 1 ~ "100% Credit",
            percent != 1 ~ paste0("Schoemann portion ", scales::dollar(budget_me)),
            .default = "Affiliated researcher"
        ),
        colabs = case_when(
            affiliated == 1 & !is.na(collaborators) ~ paste(paste0("PI: ", collaborators), amount, sep = '. '),
            affiliated == 0 & !is.na(collaborators) ~ paste(paste0("With ", collaborators), amount, sep = '. '),
            .default = amount
        ),
        period = paste0(period, '.')
    ) |> 
    arrange(desc(submitted))


# grants_ex <- grants %>%
#     filter(external == 1)
# grants_ex_pi <- grants_ex %>%
#     filter(pi == 1)
# grants_ex_copi <- grants_ex %>%
#     filter(pi == 0)
grants_internal <- grants |> 
    filter(external == 0, pi == 1)
grants_affiliated <- grants |> 
    filter(affiliated == 1)

# total <- scales::dollar(sum(grants_ex$budget_total))
# total_ex_pi <- scales::dollar(sum(grants_ex_pi$budget_managed))
```


## Internal Grants

```{r}
#| results: asis

make_grants_list(grants_internal)
```


## Affiliated Grants
```{r}
#| results: asis

make_grants_list(grants_affiliated)
```


<!-- ## Affiliated Grants -->


# Honors / Awards

```{r}
awards <- get_cv_sheet('awards') |> 
    filter(!is.na(date)) |> 
    arrange(desc(date)) |> 
    mutate(
        citation = paste0(date, ": ", description, '.'))
```

```{r}
#| results: asis

awards %>%
  filter(category != 'student') %>%
  pull(citation) %>%
  make_bullet_list()
```


# Service

```{r}
service <- get_cv_sheet('service') |> 
    filter(!is.na(date_start)) |> 
    arrange(desc(date_start)) |> 
    mutate(
        dates = case_when(
            !is.na(date_start) & !is.na(date_stop) ~ paste0(date_start, ' - ', date_stop),
            !is.na(date_start) & is.na(dates) ~ paste0(date_start, ' - present'),
            .default = dates
        ),
        citation = paste0(activity, ' (', dates, ').')
    )
```


## Faculty Service
```{r}
#| results: asis

make_ordered_list_filtered(service, "faculty")
```


## Professional Service
```{r}
#| results: asis

make_ordered_list_filtered(service, "professional")
```


## Peer Reviewer

\begin{center}
Completed 24 journal reviews (2019 - present)

\textit{List of Journals}
\end{center}

```{r}
#| results: asis

journals <- get_cv_sheet('reviews') |> 
    filter(category == 'journal') |> 
    arrange(org) |> 
    pull(org) |> 
    str_replace_all('and', '&')

n_journals <- length(journals)
if (n_journals %% 2 != 0) {
    journals[n_journals + 1] <- ""
    n_journals <- length(journals)
}
stop <- round(n_journals/2)

df <- tibble(
  j1 = journals[1:stop],
  j2 = journals[(stop + 1):n_journals]
)

rows <- apply(df, 1, function(row) {
  paste(row, collapse = " & ")
})

table_latex <- paste0(
  "\\begin{tabular}{@{}p{8.5cm}p{8.5cm}@{}}\n",
  paste(rows, collapse = " \\\\\n"),
  "\n\\end{tabular}"
)

table_latex <- paste0(
  "\\renewcommand{\\arraystretch}{1.0}\n",
  "\\setlength{\\tabcolsep}{4pt}\n",
  table_latex
)

cat(table_latex)
```


# Continuing Education

```{r}
edu <- get_cv_sheet('education') |> 
    filter(!is.na(date_start)) |> 
    arrange(desc(date_start)) |> 
    mutate(
        dates = case_when(
            !is.na(date_start) & !is.na(date_stop) ~ paste0(date_start, ' - ', date_stop),
            !is.na(date_start) & is.na(dates) ~ paste0(date_start, ' - present'),
            .default = dates
        ),
        host = if_else(is.na(host), '', paste0(', ', host)),
        citation = paste0(activity, host, ' (', dates, ').')
    )
```

```{r}
#| results: asis

edu |> 
    pull(citation) |> 
    make_ordered_list()
```


# Skills

-   **Language**: German (*native language*), English (*fluent*), French (*basic*), Spanish (*basic*).
-   **Data Collection**: Survey Design, Experiment Design (behavioral, mouse cursor tracking, eye tracking), Systematic Search (for meta study/analysis).
-   **Modeling & Analysis**: Computational Cognitive Modeling, Discrete Choice Modeling, Resampling, Optimization, Regression, Time Series.
-   **Programming**: R, MatLab, LaTeX, Markdown, Java
-   **Technologies**: Quarto, Git/GitHub, OSF, REDCap, ORSEE, OpenSesame


# Referees

\begin{tabular}{@{}p{6.5cm}p{9.5cm}@{}}
\textbf{Prof. Jacob L. Orquin, PhD} & \textbf{Prof. Dr. Stefan Scherbaum} \\[5pt]
Department of Management & Psychological Research Methods and Cognitive Modelling \\
Aarhus University & TUD Dresden University of Technology \\
Fuglesangs Allé 4 & Zellescher Weg 17 \\
DK-8210, Aarhus V, Denmark & D-01069, Dresden Germany \\
{\large\Letter} jalo[at]mgmt.au.dk & {\large\Letter} stefan.scherbaum[at]tu-dresden.de
\end{tabular}

<!-- \textbf{Prof. Jacob L. Orquin, PhD}   -->
<!-- Department of Management   -->
<!-- Aarhus University   -->
<!-- Fuglesangs Allé 4   -->
<!-- DK-8210, Aarhus V, Denmark   -->
<!-- jalo[at]mgmt.au.dk -->

<!-- \vspace{1em} -->

<!-- \textbf{Prof. Dr. Stefan Scherbaum}   -->
<!-- Psychological Research Methods and Cognitive Modelling   -->
<!-- TUD Dresden University of Technology   -->
<!-- Zellescher Weg 17   -->
<!-- D-01069, Dresden Germany   -->
<!-- stefan.scherbaum[at]tu-dresden.de -->

<!-- \vspace{1em} -->

<!-- \textbf{Dr. Frank Renkewitz}   -->
<!-- Empirical Research Methods and Statistics   -->
<!-- University of Erfurt   -->
<!-- Nordhäuser Str. 63   -->
<!-- D-99089, Erfurt Germany   -->
<!-- frank.renkewitz[at]uni-erfurt.de -->

<!-- {{< include code/_researchportfolio.qmd >}} -->
<!-- {{< include code/_teachingportfolio.qmd >}} -->
<!-- {{< include code/_previousresearch.qmd >}} -->
